Reliable feature point matching

### 2013-08-05 text/thesis.tex
Included figure for panorama

To demonstrate the usefulness of \emph{MMC} applied to panorama 
recognition and alignment we construct a simple panorama stitcher taking
as input a set of $n$ source images $\left{I_0, \ldots, I_n\right}$ and 
returns as output a panoramic image stitched together from the source 
images. Based on the matches found by applying \emph{MMC} to $I$, the 
images are combined in an order corresponding to how many matches 
connect them, as done by Brown and Lowe \cite{brown2007automatic}.

@@

>>>>

To demonstrate the usefulness of \emph{MMC} applied to panorama 
recognition and alignment we construct a simple panorama stitcher taking
as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
and returns as output a panoramic image stitched together from the 
source images. Based on the matches found by applying \emph{MMC} to $I$, 
the images are combined in an order corresponding to how many matches 
connect them, as done by Brown and Lowe \cite{brown2007automatic}.

@@

\begin{figure}[h]
	\begin{subfigure}[t]{0.8\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{images/pano_narrow}
		\caption{Source images}
		\label{fig:pano_images}
	\end{subfigure}%
	\\
	\centering
	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth]{images/panorama-autostitch}
		\caption{Panorama by Autostitch}
		\label{fig:pano_autostitch}
	\end{subfigure}%
	~%add desired spacing between images, e. g. ~, \quad, \qquad
	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth]{images/panorama-MMC}
		\caption{Panorama by MMC}
		\label{fig:pano_MMC}
	\end{subfigure}%
	\caption{An example of a difficult case of panorama recognition and 
		alignment.  In a) the source images used to generate the 
		panorama are displayed.\ b) shows the result of the Autostitch 
		program from \cite{brown2007automatic} which fails to combine 
		all images, while c) demonstrates the result of the simple 
		panorama stitcher
	using the proposed MMC algorithm. Here the two left images are 
correctly linked}
	\label{fig:pano_example}
\end{figure}
